---
title: "<center>Citation in Rmarkdown file</center>"
author: "<center>By: Wyclife Agumba Oluoch (wyclifeoluoch@gmail.com)</center>"
date: "<center>`r Sys.time()`</center>"
bibliography: [bib/cited.bib, bib/packages.bib]
link-citations: yes
nocite: '@*'
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, echo = F, warning = F, include = F, message = FALSE}

packages <- c('base', 'knitr', 'rmarkdown', 
              'tidyverse', 'here', 'todor', 
              'lintr', 'DT', 'kableExtra', 
              'roxygen2', 'testthat', 'usethis',
              'devtools', 'tinytex'
              )

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}

# Loading libraries
lapply(packages, library, character.only = TRUE) |> invisible()
```

```{r write_bib, echo = F, warning = F, include = F, message = F}

knitr::write_bib(c(
  .packages(), packages
), 'bib/packages.bib')
```

# About this article

I demo how to include citations of `R` packages and/or external sources of literature within `Rmarkdown` file in `R` [@R-base]. Some of the packages include `tidyverse` version `r packageVersion('tidyverse')` [@R-tidyverse]. I also used external citations which are not necessary packages [_sensu_ @naimi2016sdm, pp.3; @naimi2014positional]. Similarly, Naimi [-@naimi2016sdm] showed that predictor variables should be scaled to ease interpretation of the variable importance values. @soberon2004biodiversity [pp. 25] had shown similar patterns.

the codes for .Rmd and other files on my [gitHub](https://github.com/Wycology/citation) repository. 

# References