---
title: "<center>Citation in Rmarkdown file demonstration</center>"
author: "<center>Wyclife Agumba Oluoch (wyclifeoluoch@gmail.com)</center>"
date: "<center>`r Sys.time()`</center>"
bibliography: [bib/cited.bib, bib/packages.bib]
nocite: '@*'
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libs, message = FALSE}
# Package names
packages <- c('tidyverse',
              'here',
              'knitr',
              'rmarkdown',
              'todor',
              'lintr',
              'DT',
              'kableExtra',
              'roxygen2',
              'testthat',
              'usethis',
              'devtools'
              )
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}

# Package loading
lapply(packages, library, character.only = TRUE) |>
  invisible()
```

```{r write_bib}
# Automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), packages
), 'bib/packages.bib')
```
# Introduction

In this short article, I demonstrate how to cite R packages and other sources of literature within Rmarkdown file in R [@R-base]. Some of the packages include `tidyverse` version `r packageVersion('tidyverse')` [@R-tidyverse]. On the other hand, I also used citations which are not necessary packages [_sensu_ @naimi2016sdm, pp.3; @naimi2014positional]. On the same note, Naimi [-@naimi2016sdm] suggested that predictor variables should be scaled to enable interpretation of variable importance values. @soberon2004biodiversity [pp. 25] had seen similar patterns earlier. 

# References