---
title: "<center>Citation in Rmarkdown file demonstrat</center>"
author: "<center>By: Wyclife Agumba Oluoch (wyclifeoluoch@gmail.com)</center>"
date: "<center>`r Sys.time()`</center>"
bibliography: [bib/cited.bib, bib/packages.bib]
link-citations: yes
nocite: '@*'
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, echo = F, warning = F, include = F, message = FALSE}

packages <- c('base',
              'knitr',
              'rmarkdown',
              'tidyverse',
              'here',
              'todor',
              'lintr',
              'DT',
              'kableExtra',
              'roxygen2',
              'testthat',
              'usethis',
              'devtools',
              'tinytex'
              )

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}

# Loading libraries
lapply(packages, library, character.only = TRUE) |> invisible()
```

```{r write_bib, echo = F, warning = F, include = F, message = F}

knitr::write_bib(c(
  .packages(), packages
), 'bib/packages.bib')
```

# About this post

I show citation of `R` packages and/or external sources of literature within `Rmarkdown` file in `R` [@R-base]. Some of the packages include `tidyverse` version `r packageVersion('tidyverse')` [@R-tidyverse]. On the other hand, I also used external citations which are not necessary packages [_sensu_ @naimi2016sdm, pp.3; @naimi2014positional]. On the same note, Naimi [-@naimi2016sdm] suggested that predictor variables should be scaled to enable interpretation of variable importance values. @soberon2004biodiversity [pp. 25] had shown similar patterns earlier.

the codes for .Rmd and other files on my [gitHub](https://github.com/Wycology/citation) repository. 


# References